Approximation as Differentiation notes

### 2025-02-10 notes/definitions.tex
Some progress.

\noindent Equivalently $\Fam(I,C)$ is the functor category $\Func{I}{C}$ where we interpret $I$ as a discrete
category. $\Fam(-,C): \Set^{\op} \to \Cat$ is a functor which sends any set $I$ to the category $\Fam(I,C)$
and any function $f: I \to J$ to the \emph{reindexing functor} $\reindex{-}{f}: \Fam(J,C) \to \Fam(I,C)$.

\begin{definition}[Reindexing]
For any $f: I \to J$ the \emph{reindexing} functor sends any $J$-indexed family $X$ to the $I$-indexed family
$X[f]$ where $X[f]_i = X_{f(i)}$ for any $i \in I$.
\end{definition}

@@

For a functor $F: D \to \Cat$, we have the Grothendieck construction for $F$ which is the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $D$ and an $I$-indexed family $X \in FI$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $D$ where $(Ff)(X) = Y$.
\end{itemize}

\noindent The fibred category $\Fam(C)$ over $\Set$ is the Grothendieck construction for the functor
$\Fam(-,C)$:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with morphisms $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}

>>>>

\noindent Equivalently $\Fam(I,C)$ is the functor category $\Func{I}{C}$ where we interpret $I$ as a discrete
category. $\Fam(-,C): \Set^{\op} \to \Cat$ is a functor which sends any set $I$ to $\Fam(I,C)$ and any
function $f: I \to J$ to the \emph{reindexing functor} $\reindex{-}{f}: \Fam(J,C) \to \Fam(I,C)$.

\begin{definition}[Reindexing]
For any $f: I \to J$ the \emph{reindexing} functor sends any $J$-indexed family $X$ to the $I$-indexed family
$X[f]$ where $X[f]_i = X_{f(i)}$ for any $i \in I$ and similarly for morphisms.
\end{definition}

@@

For a functor $F: D \to \Cat$, the Grothendieck construction for $F$ is the category where:
\begin{itemize}
\item objects are pairs $(I, X)$ of an object $I$ of $D$ and an object of $FI$;
\item morphisms from $(I, X)$ to $(J, Y)$ are morphisms $f: I \to J$ in $D$ paired with a morphism $(Ff)(X) \to Y$.
\end{itemize}

\noindent The fibred category $\Fam(C)$ over $\Set$ is the Grothendieck construction for the functor
$\Fam(-,C): \Set^{\op} \to \Cat$:
\begin{itemize}
\item objects are pairs $(I, X)$ of a set $I$ and indexed family $X$ in $\Fam(I,C)$;
\item morphisms from $(I, X)$ to $(J, Y)$ are functions $f: I \to J$ paired with morphisms $X \to Y[f]$ in
$\Fam(I,C)$.
\end{itemize}
